Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
throw another figure in (stellar BB)
yolo

\section{\rev{Photon Number Fluxes and Energy Fluxes}}\label{appendix:photon_vs_energy_flux}
\rev{The \gls{NUV} fluxes we used in our simulations are given in units of energy flux, i.e., \si{\erg\per\second\per\centi\meter\squared}, due to their availability across different spectral types and evolutionary stages of stars.
Here, we assess the robustness of our conclusions when considering photon number fluxes instead.
}
\rev{We first computed blackbody spectral energy distributions (SEDs) for representative effective temperatures corresponding to K-type, early M-type, and late M-type stars, and across the evolutionary stages considered in the main text.
While blackbody SEDs are not necessarily representative of M-dwarf SEDs in the \gls{NUV}~\citep{Seager2013,Rugheimer2015}, the spectrally resolved evolution of M-dwarf SEDs as a function of age is not known; we therefore adopt this simplified prescription for the purpose of this sensitivity test.
We then normalized these SEDs to align with the observed UV fluxes from \citet{Richey-Yowell2023} and used them to calculate mean number flux densities (photons \si{\per\centi\meter\squared\per\second\per\nano\meter}) in the \SIrange{200}{280}{\nano\meter} wavelength range.}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{figures/combined_fluxes.pdf}
    \caption{\rev{Comparison of \gls{NUV} flux evolution in terms of photon number flux and energy flux for K-type, early M-type, and late M-type stars.
    In both regimes, later spectral types exhibit higher maximum values.
    The ratio of the maximum past \gls{NUV} fluxes in K dwarfs and late M dwarfs is slightly larger in the photon number flux regime compared to the energy flux regime, suggesting that our conclusions regarding the impact of host star spectral type on the UV Threshold Hypothesis are conservative.
    }}
    \label{fig:combined_fluxes}
\end{figure*}
\rev{We found that the derived flux densities for all considered spectral types exceed the threshold estimated by \citet{Rimmer2018} during earlier stages of stellar evolution (Figure~\ref{fig:combined_fluxes}).
Notably -- as in the case of energy fluxes -- later spectral types exhibit higher maximum past \gls{NUV} number flux densities.}

>>>>

\section{\rev{Photon Number Fluxes and Energy Fluxes}}\label{appendix:photon_vs_energy_flux}
\rev{The \gls{NUV} fluxes we used in our simulations are given in units of energy flux, i.e., \si{\erg\per\second\per\centi\meter\squared}, due to their availability across different spectral types and evolutionary stages of stars.
Here, we assess the robustness of our conclusions when considering photon number fluxes instead.
}
\rev{We first computed blackbody spectral energy distributions (SEDs) for representative effective temperatures corresponding to K-type, early M-type, and late M-type stars, and across the evolutionary stages considered in the main text.
While blackbody SEDs are not necessarily representative of M-dwarf SEDs in the \gls{NUV}~\citep{Seager2013,Rugheimer2015}, the spectrally resolved evolution of M-dwarf SEDs as a function of age is not known; we therefore adopt this simplified prescription for the purpose of this sensitivity test.
We then normalized these SEDs to align with the observed UV fluxes from \citet{Richey-Yowell2023} and used them to calculate mean number flux densities (photons \si{\per\centi\meter\squared\per\second\per\nano\meter}) in the \SIrange{200}{280}{\nano\meter} wavelength range }\revv{(see Figure~\ref{fig:normalized_photon_seds})}.

\begin{figure*}[htb]
    \centering
    \includegraphics[width=.9\textwidth]{figures/normalized_photon_seds.pdf}
    \caption{\revv{Photon flux densities of K-type, early M-type, and late M-type stars at different ages.
    All flux densities are normalized to the observed \gls{NUV} fluxes from \citet{Richey-Yowell2023}.
    The green area indicates the \SIrange{200}{280}{\nano\meter} wavelength range used to calculate energy fluxes.
    }}
    \label{fig:normalized_photon_seds}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{figures/combined_fluxes.pdf}
    \caption{\rev{Comparison of \gls{NUV} flux evolution in terms of photon number flux and energy flux for K-type, early M-type, and late M-type stars.
    In both regimes, later spectral types exhibit higher maximum values.
    The ratio of the maximum past \gls{NUV} fluxes in K dwarfs and late M dwarfs is slightly larger in the photon number flux regime compared to the energy flux regime, suggesting that our conclusions regarding the impact of host star spectral type on the UV Threshold Hypothesis are conservative.
    }}
    \label{fig:combined_fluxes}
\end{figure*}
\rev{We found that the derived flux densities for all considered spectral types exceed the threshold estimated by \citet{Rimmer2018} during earlier stages of stellar evolution (Figure~\ref{fig:combined_fluxes}).
Notably -- as in the case of energy fluxes -- later spectral types exhibit higher maximum past \gls{NUV} number flux densities }\revv{due to the steeper rise of the blackbody SEDs at shorter wavelengths}.
